Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-22 paper/structureScene.tex
define S_2 x

Among auditory scenes, amplitude modulations may be caused by a broad variety of mechanical interactions, including collision, friction, and turbulent flow.
They also account for some higher-level cognitive attributes of sound, \eg prosody in speech or rhythm in music.

In all subsequent experiments, wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as a fourth-order Gammatone
wavelet with one vanishing moment \cite{Venkitaraman2014}.

>>>>

Among auditory scenes, amplitude modulations may be caused by a broad variety of mechanical interactions, including collision, friction, and turbulent flow.
They also account for some higher-level cognitive attributes of sound, \eg prosody in speech or rhythm in music.
Although they are discarded while filtering $\boldsymbol{x_1}(t,\gamma_1)$ into a translation-invariant representation $\mathbf{S_1}\boldsymbol{x}(t,\gamma_1)$, they can be recovered by a second wavelet transform modulus operator.
The amplitude modulation spectrum resulting from this operator is
\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2) =
\vert \boldsymbol{x_1} \ast \boldsymbol{\psi_{\gamma_2}} \vert(t,\gamma_1),
\end{equation}
where the center frequencies of the wavelets $\boldsymbol{\psi_{\gamma_2}}(t)$ are of the form $2^{-\gamma_2/Q_2} \xi_2$, and the second-order log-frequency index $\gamma_2$ takes integer values between $0$ and $(J_2 \times Q_2 - 1)$.
In the sequel, we set $\xi_2$ to $2.5\,\mathrm{kHz}$, $Q_2$ to $1$, and $J_2$ to $12$.
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2) =
(\boldsymbol{x_2} \ast \phi)(t,\gamma_1,\gamma_2).
\end{equation}
In all subsequent experiments, wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as a fourth-order Gammatone
wavelet with one vanishing moment \cite{Venkitaraman2014}.
